Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 paper/paper.tex
First pass of chapter 6 (minus survey results)
Fixing math

\usepackage[dvipsnames]{xcolor}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{listings}
\DeclareCaptionFont{white}{ \color{white} }
\DeclareCaptionFormat{listing}{
  \colorbox[cmyk]{0.43, 0.35, 0.35,0.01 }{
    \parbox{\textwidth}{#1#2#3}
  }
}
\captionsetup[lstlisting]{ format=listing, labelfont=white, textfont=white, singlelinecheck=false, margin=0pt, font={bf,footnotesize} }

@@

\title{Combining Linked data and Data Mining Techniques to improve Clustering of Large Scale Media Repositories: A case study with BBC}
%\subtitle{[Extended Abstract]

\numberofauthors{3}
\author{
\alignauthor
Ross Fenning\\
       \affaddr{British Broadcasting Corporation (BBC)}\\
       \affaddr{MediaCityUK}\\
       \affaddr{Salford, United Kingdom}\\
       \email{ross.fenning@bbc.co.uk}
\alignauthor
Dhavalkumar Thakker\\
       \affaddr{University of Bradford}\\
       \affaddr{Bradford}\\
       \affaddr{United Kingdom}\\
       \email{dhavalkumar.thakker@gmail.com}
\alignauthor Tejal Shah\\
       \affaddr{UNSW}\\
       \affaddr{Australia}\\
       \email{tejals@cse.unsw.edu.au}
}

\maketitle
\begin{abstract}
Media companies produce ever larger numbers of articles, videos, podcasts,
games, commonly collectively known as ``content''. A successful
content-producing organisation not only has to develop systems to aid producing
and publishing content, but there are also demands to engineer effective
mechanisms to aid consumers in finding that content. Linked Data technologies
provide data enrichment beyond attributes and keywords explicitly available
within content data or metadata. In our work we experiment with a
plausible mapping of an RDF graph representing a content item to an attribute
set suitable for data mining. With such a mapping, we have explored the
application of machine learning, particularly unsupervised learning, across
an organisation's whole content corpus. We have created an innovative pipeline
of linked data and data mining that allows clustering of media content items on
the fly. We have evaluated such system in the context of website content
produced by the British Broadcasting Corporation (BBC) and present the optimum
combination of RDF graphs and data mining with qualitative and quantitative
results.
\end{abstract}

\keywords{Semantics; Linked Data; Semantic Web; Machine Learning; Clustering; Data Mining; RDF Graph; Media repositories; Content Management}

@@

\subsection{Problem}

In order to build systems
that operate across the full corpus of their content, organisations face
several problems:

@@

\item Large organisations can have content across multiple content management
systems, in differing formats and data models.

\item Many content items are in fairly opaque formats, e.g. video content may be
stored as audio-visual binary data with minimal, textual metadata to display on
a containing web page.

\item Content is being published continuously, which means any search or
discovery system needs to keep up with content as it is published and process it
into the appropriate data structures. Any analytical process that operates
over all content (e.g. machine learning) may need to be run periodically or in
an incremental fashion.

@@

The following hypotheses are proposed for gaining new insights about an
organisation's diverse corpus of content:

@@

\item Research and software tools around the concept of \emph{Linked Data} can
aid us in rapidly acquiring a broad view (perhaps at the expense of depth) of an
organisation's content whilst also providing a platform for simple enrichment of
that content's metadata.

\item We can establish at least a na\"ive mapping of an RDF graph representing a
content item to an attribute set suitable for data mining. With such a mapping,
we can explore applying machine learning across an organisation's whole content
corpus.

@@

\item Many content-producers currently enrich their web pages with small
amounts of semantic metadata to provide better presentation of that content
as it is shared on social media. This enables simple collection of a full
breadth of content with significantly less effort than direct integration
with content management systems (i.e. Enterprise Integration).

@@

Notably, Kiefer, Bernstein and Locher\cite{kiefer2008adding} proposed a novel
approach called SPARQL-ML -- an extension to the
SPARQL\cite{segaran2009programming} query language with new keywords to
facilitate both generating and applying models. This means that the system
capable of parsing and running standard queries must also run machine learning
algorithms.

Their work involved developing an extension to the SPARQL query
engine for \emph{Apache Jena}\footnote{https://jena.apache.org/} that integrates
with systems such as \emph{Weka}\footnote{http://www.cs.waikato.ac.nz/ml/weka/}.
A more suitable software application for enterprise use might focus solely on
converting RDF graphs into a neutral data structure that can plug into arbitrary
data mining algorithms.

An approach of generating attributes for a given resource was proposed by
Paulheim and F\"urnkranz\cite{paulheim2012unsupervised}. They defined specific
SPARQL queries and provided case study evidence for the effectiveness of
each strategy.

Their work focused on starting with relational-style data (e.g. from a
relational database) and using \emph{Linked Open Data} to identify entities
within literal values in those relations and generated attributes from
SPARQL queries over those entities.

For a large content-producer, there is a more general problem where many content
items do not have a relational representation and the content source is a body
of text or even a raw HTML page. However, the feature generation from Paulheim
and F\:urnkranz proves to be a promising strategy given we can acquire an RDF
graph model for content items in the first place.

@@

With the knowledge only of a content item's IRI, we are arguably only able to
produce an empty named RDF graph. Such a graph for an example IRI
\texttt{http://example.com/entity/} is illustrated in
JSON-LD syntax in Listings~\ref{lst:jsonld-identity}. This provides our
base case in the inductive design.

Paulheim and F\"urnkranz\cite{paulheim2012unsupervised} described a number of
SPARQL queries for generating feature sets from RDF data, inspired
a simple query such as that shown in Listings~\ref{lst:simple-sparql}. This
query generates a boolean \texttt{true} value for any properties that match
and implies \texttt{false} for those that do not and we then flatten this into
a simple feature format: \texttt{?p\_?o=true},
e.g. \texttt{rdf:type\_schema:Article=true}

@@

Finally, an additional layer of indirection was created

@@

%\bibliographystyle{abbrv}
%\bibliography{../report/references}

>>>>

\usepackage[autosize]{dot2texi}
\usepackage[dvipsnames]{xcolor}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{listings}

@@

\title{Improving content discovery through combining linked data and data mining techniques}
%\subtitle{[Extended Abstract]

\numberofauthors{1}
\author{
\alignauthor
Ross Fenning\\
       \affaddr{British Broadcasting Corporation (BBC)}\\
       \affaddr{MediaCityUK}\\
       \affaddr{Salford, United Kingdom}\\
       \email{ross.fenning@bbc.co.uk}
}

\maketitle
\begin{abstract}
A comparative study of multiple approaches for extracting linked data
from web content published by the BBC for the purposes of applying
machine learning to cluster related content.

This project designs and implements a process by which semantic data
about any piece of online media content can be extracted into RDF
models in
multiple ways and feature
sets for machine learning can be generated from
that data. The clusters produced by fourteen different permutations
of techniques are evaluated and a potential application of suggesting
related content is mocked up for qualitative evaluation.

It is concluded organisations can very easily make use of
embedded semantics within web pages due to better semantic properties
being made available in recent years because of pressure from
social media sites such as Facebook and Twitter.
These embedded semantics provide a good baseline for simple
learning that can group content based on broad categorisation.

A simple application of entity extraction also shows promising results in
evaluation and is highlighted as an area for organisations to explore
tuning to provide a powerful complement to embedded semantics.
\end{abstract}

@@

\subsection{Problems}

@@

\item Content across multiple content management
systems, in differing formats and data models.

\item Content items are in fairly opaque formats, e.g. video and audio content.

\item Content is being published continuously, so any analytical process that operates
over all content (e.g. machine learning) may need to be run periodically or in
an incremental fashion.

@@

@@

\item Research and software tools around the concept of \emph{Linked Data} can
aid us in rapidly acquiring a broad view of an
organisation's content.

\item We can establish at least a na\"ive mapping of an RDF graph representing a
content item to an attribute set suitable for data mining.

@@

\item We can make use of semantic metadata added to pages
to provide better presentation of that content as it is shared on social media.

@@

For a large content-producer, there is a more general problem where many content
items do not have a relational representation and the content source is a body
of text or even a raw HTML page. However, the feature generation from Paulheim
and F\"urnkranz proves to be a promising strategy given we can acquire an RDF
graph model for content items in the first place.

@@

Listings~\ref{lst:simple-sparql} shows a SPARQL query inspired by Paulheim and F\"urnkranz\cite{paulheim2012unsupervised}.
This
query generates a boolean \texttt{true} value for any properties that match
and implies \texttt{false} for those that do not and we then flatten this into
a simple feature format: \texttt{?p\_?o=true},
e.g. \texttt{rdf:type\_schema:Article=true}

@@

With a feature generation strategy in place, we can inductively build up the
pipeline of how we create RDF graphs for that generation.

With the knowledge only of a content item's IRI, we are arguably only able to
produce an empty named RDF graph. Such a graph for an example IRI
\texttt{http://example.com/entity/} is illustrated in
JSON-LD syntax in Listings~\ref{lst:jsonld-identity}. This provides our
base case in the inductive design. This enables a \emph{null} pipeline
as shown in Figure~\ref{fig:gen-null}.

            \begin{figure}[h]
              \begin{center}
                \begin{dot2tex}[dot,options=-t math,autosize,pgf,scale=0.7]
                  digraph g {
                    rankdir=LR;

                    node [shape=circle,margin="0,0"];
                    edge [len=2];

                    IRI -> RDF [label="extract"];
                    RDF -> Features [label="(IRI)"];
                  }
                \end{dot2tex}
              \end{center}
              \caption{Null feature generator \label{fig:gen-null}}
            \end{figure}

We can then add in, one-by-one, the following potential extraction techniques:

\begin{itemize}
\item Extraction by dereference of the IRI, parsing any RDFa or microdata
semantics found embedded in the response.
\item Use entity extraction such as DBpedia and infer triples of the form
$(IRI, rdf\!\!:\!\!about, Entity)$
\item Infer a relationship between pages if they have hyperlinks to each
other: $(IRI_1, ex:related, IRI_2)$
\end{itemize}

We also propose enrichment techniques such as the following:

\begin{itemize}
\item Dereference every object IRI for triples of which the given content item
is the subject.
\item Infer facts based on OWL/RDFS ontologies and schemas, e.g. infer an
item is about animals if the entity \emph{Dog} is found and we have an
ontology that states that \emph{Animal} is a superclass.
\end{itemize}

@@

\bibliographystyle{abbrv}
\bibliography{../report/references}

### 2016-05-06 report/chapters/03-design.tex
Fixing math

\begin{displaymath}
(IRI_{1}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)\\
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)
\end{displaymath}

@@

\begin{displaymath}
(IRI_{1}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)\\
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)\\
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)
\end{displaymath}

>>>>

\begin{displaymath}
(IRI_{1}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)\\
\end{displaymath}
\begin{displaymath}
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)
\end{displaymath}

@@

\begin{displaymath}
(IRI_{1}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)\\
\end{displaymath}
\begin{displaymath}
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)\\
\end{displaymath}
\begin{displaymath}
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)
\end{displaymath}
